---
title: "Gold standard inspection"
output:
  pdf_document:
    fig_caption: yes
    toc: True
  html_document:
    fig_caption: yes
    fig_width: 8
---

# Inspection of the existing data from Hollink et al.

Loading libraries
```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
```

## Datasets from Hollink et al.
```{r echo=TRUE, message=FALSE, warning=FALSE}

annotator1_tools <- read_delim("handtool_labelled.csv", col_names =
                                 c('lvl1_synset','lvl2_synset','lvl3_synset',
                                  'lvl4_synset','lvl5_synset','lvl6_synset',
                                  'isBasic','isFamiliar','isUnsure','note',
                                  'inHistWords','note2'), skip=1, delim=';')

annotator1_fruits <- read_delim("ediblefruit_labelled.csv", col_names =
                                  c('lvl1_synset','lvl2_synset','lvl3_synset',
                                  'lvl4_synset','lvl5_synset','lvl6_synset',
                                  'isBasic','isFamiliar','isUnsure','note',
                                  'inHistWords'), skip=1, delim=';')

annotator1_instruments <- read_delim("musicalinstrument_labelled.csv", col_names =
                                  c('synonyms','glossary','lvl1_synset',
                                  'lvl2_synset','lvl3_synset','lvl4_synset',
                                  'lvl5_synset','lvl6_synset','lvl7_synset',
                                  'lvl8_synset','isBasic','isFamiliar','isUnsure',
                                  'notes'), skip=1, delim=';')

annotator2_tools <- read_delim("handtool_a2.csv",
                               col_names=c('synonyms','glossary','lvl1_synset',
                                  'lvl2_synset','lvl3_synset','lvl4_synset',
                                  'lvl5_synset','lvl6_synset','isBasic','origin',
                                  'isFamiliar','isUnsure','notes'), skip=1, delim=',')

annotator3_tools <- read_delim("handtool_a3.csv",
                               col_names=c('synonyms','glossary','lvl1_synset',
                                  'lvl2_synset','lvl3_synset','lvl4_synset',
                                  'lvl5_synset','lvl6_synset','isBasic','isFamiliar',
                                  'isUnsure','notes'), skip=1, delim=',')
```

### Cleaning up dataframe layout
* reduce hierarchy lvl columns to 2 dim
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Function to create new columns for synsets
red_lvls <- function(ds, synlen = 6, dflen){
  ds_copy <- ds
  synsets <- c()
  tree_depth <- c() 
  tree <- c("","","","","","","","")
  ancestors <- c()
  
  for (i in 1:length(ds$lvl1_synset)){
    if(!is.na(ds[["lvl1_synset"]][i])){
      syn <- toString(ds[["lvl1_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 1)
  
      tree[1] <- syn
      ancestors <- append(ancestors, "root")
    }
    else if(!is.na(ds[["lvl2_synset"]][i])){
      syn <- toString(ds[["lvl2_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 2)
      
      tree[2] <- syn
      ancestors <- append(ancestors, tree[1])
      
    }
    else if(!is.na(ds[["lvl3_synset"]][i])){
      syn <- toString(ds[["lvl3_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 3)
      
      tree[3] <- syn
      ancestors <- append(ancestors, tree[2])
    }
    else if(!is.na(ds[["lvl4_synset"]][i])){
      syn <- toString(ds[["lvl4_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 4)
      
      tree[4] <- syn
      ancestors <- append(ancestors, tree[3])
    }
    else if(!is.na(ds[["lvl5_synset"]][i])){
      syn <- toString(ds[["lvl5_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 5)
      
      tree[5] <- syn
      ancestors <- append(ancestors, tree[4])
    }
    else if(!is.na(ds[["lvl6_synset"]][i])){
      syn <- toString(ds[["lvl6_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 6)
      
      tree[6] <- syn
      ancestors <- append(ancestors, tree[5])
    }
    else if(!is.na(ds[["lvl7_synset"]][i]) & synlen > 6){
      syn <- toString(ds[["lvl7_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 7)
      
      tree[7] <- syn
      ancestors <- append(ancestors, tree[6])
    }
    else if(!is.na(ds[["lvl8_synset"]][i]) & synlen > 7){
      syn <- toString(ds[["lvl8_synset"]][i])
      synsets <- append(synsets, syn)
      tree_depth <- append(tree_depth, 8)
      
      tree[8] <- syn
      ancestors <- append(ancestors, tree[7])
    }
    #needs optional lvl 7 and 8, see optional parameters
    else{
      print("Some error must have occured.")
      print(ds[['synonyms']][i])
    }
    
  }
  ds_copy$synsets <- synsets
  ds_copy$tree_depth <- tree_depth
  ds_copy$ancestors <- ancestors
  ds_copy
}

#adding all the new columns
annotator1_fruits <- red_lvls(annotator1_fruits)
annotator1_tools <- red_lvls(annotator1_tools)
annotator1_instruments <- red_lvls(annotator1_instruments, 8)

annotator2_tools <- red_lvls(annotator2_tools)
annotator3_tools <- red_lvls(annotator3_tools)


#Now we remove the unnecessary old columns from the dfs
#tools
bl_tools <- data.frame(matrix(ncol = 6, nrow = 164))
colnames(bl_tools) <- c('synsets', 'tree_depth', 'ancestors', 
                        'judgmt_a1', 'judgmt_a2', 'judgmt_a3')

bl_tools$synsets <- annotator1_tools$synsets
bl_tools$tree_depth <- annotator1_tools$tree_depth
bl_tools$ancestors <- annotator1_tools$ancestors
bl_tools$judgmt_a1 <- annotator1_tools$isBasic

#add judgements of other 2 annotators
bl_tools$judgmt_a2 <- annotator2_tools$isBasic
bl_tools$judgmt_a3 <- annotator3_tools$isBasic

#instruments

bl_instruments <- data.frame(matrix(ncol = 4, nrow = 192))
colnames(bl_instruments) <- c('synsets', 'tree_depth', 'ancestors', 
                              'judgmt_a1')

bl_instruments$synsets <- annotator1_instruments$synsets
bl_instruments$tree_depth <- annotator1_instruments$tree_depth
bl_instruments$ancestors <- annotator1_instruments$ancestors
bl_instruments$judgmt_a1 <- annotator1_instruments$isBasic

#fruits

bl_fruits <- data.frame(matrix(ncol = 4, nrow = 197))
colnames(bl_fruits) <- c('synsets', 'tree_depth', 'ancestors', 
                         'judgmt_a1')

bl_fruits$synsets <- annotator1_fruits$synsets
bl_fruits$tree_depth <- annotator1_fruits$tree_depth
bl_fruits$ancestors <- annotator1_fruits$ancestors
bl_fruits$judgmt_a1 <- annotator1_fruits$isBasic

```

## Inspecting new dataframes 

```{r echo=TRUE}
head(bl_tools)
```

```{r echo=TRUE}
head(bl_fruits)
```

```{r echo=TRUE}
head(bl_instruments)
```

## Quick visualization of Tools
```{r echo=TRUE, message=FALSE, warning=FALSE}
p <- ggplot(bl_tools, mapping = aes(x = tree_depth, fill = judgmt_a1)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6)) +
  labs(x="Tree depth", y="Count of synsets", 
       title="Count of tools by depth", 
       subtitle="Colored by annotator judgement.",
       caption="Figure 1.: Tools by depth, colored by judgement.")
p 

```

Datasets from Niamh Henry
```{r message=FALSE, warning=FALSE}
all_ediblefruit <- read_csv("./niamh/labels/all_ediblefruit_labelled.csv")
all_handtool <- read_csv("./niamh/labels/all_handtool_labelled.csv")
all_instrument <- read_csv("./niamh/labels/all_musicalinstruments_labelled.csv")
all_furniture <- read_csv("./niamh/labels/GoldStandard_Furniture_merged.csv")
all_garments <- read_xlsx("./niamh/labels/GoldStandard_Garments_merged.xlsx")

```

Now I can complete the two dataframes bl_fruits and _instruments with the missing annotations.
* Check if same order
* copy over annotations columns (2)
* copy over glossary and synonyms (3)

```{r message=FALSE, warning=FALSE}
issameorder1 <- (all_ediblefruit$A1_Label == bl_fruits$judgmt_a1) #True

bl_fruits$judgmt_a2 <- all_ediblefruit$Label
bl_fruits$judgmt_a3 <- all_ediblefruit$A3_Label
bl_fruits$synonyms <- all_ediblefruit$Synonyms
bl_fruits$glossary <- all_ediblefruit$Glossary

issameorder2 <- all_instrument$Label == bl_instruments$judgmt_a1 #True

bl_instruments$judgmt_a2 <- all_instrument$A2_Label
bl_instruments$judgmt_a3 <- all_instrument$A3_Label
bl_instruments$synonyms <- all_instrument$Synonyms
bl_instruments$glossary <- all_instrument$Glossary

bl_tools$synonyms <- all_handtool$Synonyms
bl_tools$glossary <- all_handtool$Glossary
```
Having both the data from Niamh and Hollink, I finally have all of the information. Niamh added the synonyms and glossary to her dataframe and she has the 2 missing anotations from the two other annotators.

The data has some formating around the synset names, they are not consistent between datasets and already lead to bugs.

```{r}
syn_stripper <- function(string){
  if(str_split(string, '')[[1]][1] != "["){
    stripped <- string
  }
  else{
    stripped <- str_split(string, '\\(')[[1]][2]
    stripped <- str_split(stripped, '\\)')[[1]][1]
    s_t_r_i_p <- str_split(stripped, "")
    stripped <- str_flatten(s_t_r_i_p[[1]][3:length(s_t_r_i_p[[1]])-1])
  }
  stripped
}
#bug: there are ' inside of the synset names..
#fixed: different extraction.


bl_fruits$synsets <- sapply(bl_fruits$synsets, syn_stripper)
bl_fruits$ancestors <- sapply(bl_fruits$ancestors, syn_stripper)

bl_instruments$synsets <- sapply(bl_instruments$synsets, syn_stripper)
bl_instruments$ancestors <- sapply(bl_instruments$ancestors, syn_stripper)

bl_tools$synsets <- sapply(bl_tools$synsets, syn_stripper)
bl_tools$ancestors <- sapply(bl_tools$ancestors, syn_stripper)

```

By visualizing the trees (below) I found that some rows in the dataset are duplicates. There are also cases where the synset column has duplicates, but some other information in the same column is different, e.g. ancestor. Removing pure duplicates is easy, but removing semi-duplicates with differing annotations is going to be tougher. I will probably have to make a list of all semi-duplicates and handpick the candidate to keep.

## Eliminating duplicates
### Function definitions
```{r}

find_total_dups <- function(df){
  dupes <- data.frame()
  dups_bools <- duplicated(df[,1:3])
  dups_pos <- which(dups_bools)
  for (x in dups_pos){
    dupes <- rbind(dupes, df[which(df$synonyms == df$synonyms[x]),])
  }
  
  dupes
  
}

find_semi_dupes <- function(df){
  dupes <- data.frame()
  
  dup_bools <- duplicated(df$synsets)
  dup_pos <- which(dup_bools)
  dup <- c()
  for (x in dup_pos){
    dup <- unique(append(dup, which(df$synonyms == df$synonyms[x])))
  }
  df[dup,]
}
  
#fruits
fruits_has_total_dup <- find_total_dups(bl_fruits) #NULL
fruits_has_semi_dup <- find_semi_dupes(bl_fruits) #2

#tools
tools_has_total_dup <- find_total_dups(bl_tools) #NULL
tools_has_semi_dup <- find_semi_dupes(bl_tools) #14

#instruments
instruments_has_total_dup <- find_total_dups(bl_instruments) #yes, 3
instruments_has_semi_dup <- find_semi_dupes(bl_instruments) # many
```
Now that I can detect complete or semi duplicates, I will handpick the rows to be eliminated from the original data.

### Fruits

```{r}
print.data.frame(fruits_has_total_dup)
```
The fruits dataset has 0 total duplicates.

```{r}
print.data.frame(fruits_has_semi_dup[,c("synsets", "ancestors","judgmt_a1","judgmt_a2","judgmt_a3")])
```
There are 2 instances of semi-duplicate concepts.
#### The currant
Currant has also been listed as a subordinate of raisin, additionally to berry. This seems superflous as the fruit is still the same fruit after drying. People only tend to call all kinds of dried berries 'raisin'.
I will remove the raisin subordinate (105).

#### The medlar
There does not seem to be any difference between both instances, except for the second one having a higher digit at the end of the name and the third annotator giving two different judgements. I will remove the one with the X judgement (149).

#### Removal
```{r}
fruits_rm <- c(105, 149)
#bl_fruits_new <- bl_fruits[-fruits_rm,]
```

### Tools
```{r}
print.data.frame(tools_has_total_dup)
```
Tools has no total duplicates.

```{r}
print.data.frame(tools_has_semi_dup[,c("synsets", "ancestors","judgmt_a1","judgmt_a2","judgmt_a3")])
```
#### Hand Shovel
RM 33

#### Coal Shovel
RM 34

#### Entrenching Tool
RM 35

#### Spade
RM 36

#### Ditch Spade
RM 37

#### Garden Spade
RM 38

#### Spud
RM 39

#### Removal
```{r}
tools_rm <- c(33:39)
#bl_tools_new <- bl_fruits[-tools_rm,]
```

### Instruments
```{r}
print.data.frame(instruments_has_total_dup[,c("synsets", "ancestors","judgmt_a1","judgmt_a2","judgmt_a3")])
```
#### Baby Grand
RM 59, 107

#### Concert Grand
RM 60, 108

#### Spinet 
RM 63, 94, 111

```{r}
print.data.frame(instruments_has_semi_dup[,c("synsets", "ancestors","judgmt_a1","judgmt_a2","judgmt_a3")])
```
#### Synthesiser
RM 32                

#### Piano
RM 57, 105

#### Grand Piano
RM 58, 106

#### Mechanical Piano
RM 61, 109

#### Upright
RM 32, 110

#### Bass fiddle
RM 71

#### Clavichord
RM 91

#### clavier
RM 92

#### Harpsichord
RM 93

#### Virginal
RM 95

#### Bass Guitar
RM 5 Because visually closer to guitar

#### Dulcimer
RM /

#### Bass Horn
RM 120

#### Euphonium
RM 121

#### Helicon
RM 122

#### Accordion
RM 133

#### Organ
RM 141

#### Bombardon
RM 180

In the case where two annotators annotated 'x', that duplicate was prefered for removal.

#### Removal
```{r}
#instruments_rm <- c(59, 107, 60, 108,63, 94, 111,32,57,105,58,106,61,109,32,110,71,91,91,93,95,5,120,121,122,133,141,180)

instruments_rm <- c(59, 107, 60, 108,63, 94, 111)
bl_instruments_new <- bl_instruments[-instruments_rm,]
```


## Export BL Dataframe
At this point we have inspected, combined and transformed the data. To use the data in the online experiment, we need all basic level concepts first. The total number of basic level concepts in each taxonomy decides over the size of the final data-set. The final experiment data set could have been assembled in this file, but it is unsure if all hyper/hyponyms are captured correctly after the data set modifications. From the csv of Hollink's previous studies it is not possible anymore to detect multiple parents.
The data needs to be checked with the NLTK Wordnet data set, which works better in Python. The dataset to be exported only needs two columns; the synset name and the judgement certainty. Only concepts that were judged as BL by at least 2 annotators should be included. The second column will thus only have 2 possible values.

The duplicate finding process above is not suited for this purpose, It only served to show me that the current data set needs to be reconstructed using the actual Wordnet Python package.

```{r}
extract_unique_bl <- function(df, full_certainy = F){
  unique_bl <- data.frame()
  
  for(i in 1:length(df[[1]])){
    synset <- df$synsets[i]
    a1 <- df$judgmt_a1[i] == 'b'
    a2 <- df$judgmt_a2[i] == 'b'
    a3 <- df$judgmt_a3[i] == 'b'
    bl_certainty <- F
    if(any(synset == unique_bl$synsets)){
      print("Duplicate:")
      print(synset)
    }
    else{
      b_votes <- length(which(c(a1,a2,a3)))
      if(b_votes == 3){
        bl_certainty <- T
        unique_bl <- rbind(unique_bl, c(synset, bl_certainty))
      }
      if(b_votes == 2 & (!full_certainy)){
        unique_bl <- rbind(unique_bl, c(synset, bl_certainty))
      }
    }
  }
  colnames(unique_bl) <- c("synset", "bl_certain")
  unique_bl
}

bl_only_handtools <- extract_unique_bl(bl_tools)
bl_only_edible_fruits <- extract_unique_bl(bl_fruits)
bl_only_musical_instruments <- extract_unique_bl(bl_instruments)

write_csv(bl_only_edible_fruits, "bl_only_edible_fruits.csv")
write_csv(bl_only_handtools, "bl_only_handtools.csv")
write_csv(bl_only_musical_instruments, "bl_only_musical_instruments.csv")

write_csv(bl_fruits, "edible_fruit.csv")
write_csv(bl_tools, "handtool.csv")
write_csv(bl_instruments, "musical_instrument.csv")

```






